### 2022-06-16 tex/supplement.tex
Add alternative choice of r prior
Notational improvements

We define the transformation $\phi: \mathbb{R}^{n-1} \to \Delta^{n}: y \mapsto x_-$, where $x=\begin{pmatrix}x_- \\ \frac{1}{r}\end{pmatrix}$, $x_i = \frac{1}{r} e^{y_i}$ for $i \in \{1, \ldots, n-1\}$, and $r = 1 + \sum_{i=1}^{n-1} e^{y_i}$.

@@

We define the transformation $\phi: \mathbb{R}^n \backslash \{0\} \to \Delta^{n-1} \times \mathbb{R}_{>0}: y \mapsto (x, r)$,
where $r = \sum_{i=1}^n e^{y_i}$ and $x_i = \frac{1}{r} e^{y_i}$.

Similar to above, to compute the density correction we use the bijective transformation $f: y \mapsto (x_-, r)$.
First we compute the scalar derivatives:

@@

which has the Jacobian

$$J = \begin{pmatrix}I_{n-1} - x_- \boldsymbol{1}_{n-1}^\top & -x_- \\ r \boldsymbol{1}_{n-1}^\top & r \end{pmatrix} \mathrm{diag}(x),$$

@@

>>>>

Let $\Delta^n$ indicate the unit $n$-simplex with $n$ positive elements that sum to 1 and $\Delta^n_-$ indicate the first $n-1$ elements, from which the final element can be uniquely determined.

We define the transformation $\phi: \mathbb{R}^{n-1} \to \Delta^n_-: y \mapsto x_-$, where $x=\begin{pmatrix}x_- \\ \frac{1}{r}\end{pmatrix} \in \Delta^n$, $x_i = \frac{1}{r} e^{y_i}$ for $1 \le i \le n-1$, and $r = 1 + \sum_{i=1}^{n-1} e^{y_i}$.

@@

We define the transformation $\phi: \mathbb{R}^n \to \Delta^{n-1} \times \mathbb{R}_{>0}: y \mapsto (x_-, r)$,
where $r = \sum_{i=1}^n e^{y_i}$ and $x_i = \frac{1}{r} e^{y_i}$ for $1 \le i \le n-1$..

First we compute the scalar derivatives:

@@

which corresponds to the Jacobian

$$J = \begin{pmatrix}I_{n-1} - x_- \boldsymbol{1}_{n-1}^\top & -x_- \\ r \boldsymbol{1}_{n-1}^\top & r \end{pmatrix} \mathrm{diag}(x).$$

@@

Alternatively, if we choose $r \sim \mathrm{Gamma}(n, 1)$, then

$$\mathrm{correction} = \pi(r) |J| = r^n e^{-r} \prod_{i=1}^n x_i = \exp\left(\sum_{i=1}^n y_i - \sum_{i=1}^n e^{y_i}\right).$$

This latter correction is equivalent to the sampling procedure from the Dirichlet distribution with $\alpha_i=1$, where $z_i \sim \mathrm{Exponential}(1)$ and $y = \frac{z}{\sum_{i=1}^n z_i}$.
